Some Title

### 2023-10-16 output/paper/manuscript.qmd
Nothing.
Just tried to compile paper.
How the fuck do I cross ref across files?
I think I fixed the cross-referencing with external files and tables at the end.

---
title: "Some Fancy Title"

@@

# Introduction {#sec-intro}
```{r}
#| child: output/paper/sections/introduction.qmd
```

# Methods {#sec-methods}
```{r}
#| child: output/paper/sections/methods.qmd
```

# Results {#sec-res}
```{r}
#| child: output/paper/sections/results.qmd
```

# Discussion {#sec-discussion}
```{r}
#| child: output/paper/sections/discussion.qmd
```

@@

>>>>

---
title: "Some Title"

@@

# Introduction {#sec-intro}

{{< include sections/introduction.qmd >}}

# Methods {#sec-methods}

{{< include sections/methods.qmd >}}

# Results {#sec-res}

{{< include sections/results.qmd >}}

# Discussion {#sec-discussion}

{{< include sections/discussion.qmd >}}

@@

{{< embed tables.qmd >}}

### 2023-10-16 output/paper/manuscript.tex
How the fuck do I cross ref across files?
I think I fixed the cross-referencing with external files and tables at the end.

@@

>>>>

Table~\ref{tbl-chem-info}

@@

\section{Tables}\label{tables}

\begin{itemize}
\tightlist
\item
  Begin each table on a new page after the list of references.
\item
  Tables may not contain parts.
\item
  Provide the title for each table above the table and the notes below
  the table.
\item
  List footnotes after the general one, one per line and indicated with
  a lowercase italicized letter.
\end{itemize}

\section{Descriptive data}\label{descriptive-data}

\subsection{Study populations}\label{study-populations}

\begin{itemize}
\tightlist
\item
  Basic characteristics of study participants (demographic, clinical,
  social), by cohort and overall.

  \begin{itemize}
  \tightlist
  \item
    Include all covariates included in primary or secondary analyses.
  \item
    Indicate number of participants with missing data for each variable
    of interest.
  \item
    Report numbers of outcome events or summary measures.
  \end{itemize}
\end{itemize}

\subsection{Endocrine disruptors}\label{endocrine-disruptors}

\begin{itemize}
\tightlist
\item
  Levels of unprocessed biomarkers (chemicals), with IDs.
\item
  Report: minimum and maximum, percentiles, and number of observations
  above/below the assay's LOD and LOQ.
\end{itemize}

\begin{table}

\caption{\label{tbl-chem-info}Information about the non-persistent
EDCs.}

\centering{

\begin{longtable}[]{@{}llllll@{}}
\toprule\noalign{}
Compound & Symbol & PubChem CID & CTD ID & Exposome Explore ID &
Parental compound \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
OP pesticide metabolites & & & & & \\
diethyl dithiophosphate & DEDTP & 9274 & C000654497 & NA & NA \\
diethyl phosphate & DEP & 654 & C034789 & NA & NA \\
diethyl thiophosphate & DETP & 3683036 & C035638 & NA & NA \\
dimethyl dithiophosphate & DMDTP & NA & Unsure & NA & NA \\
dimethyl phosphate & DMP & 13134 & C007477 & NA & NA \\
dimethyl thiophosphate & DMTP & 168140 & C040340 & NA & NA \\
Phenols & & & & & \\
bisphenol A & BPA & 6623 & C006780 & 1418 & NA \\
ethyl-paraben & ETPA & 8434 & C012313 & 1422 & NA \\
methyl-paraben & MEPA & 7456 & C015358 & 1421 & NA \\
n‑butyl‑paraben & BUPA & 7184 & C038091 & 1424 & NA \\
oxybenzone & OXBE & 4632 & C005290 & 1419 & NA \\
propyl-paraben & PRPA & 7175 & C006068 & 1423 & NA \\
triclosan & TRCS & 5564 & D014260 & 1420 & NA \\
Phthalate metabolites & & & & & \\
mono benzyl phthalate & MBzP & 31736 & C103325 & 1397 & BzBP \\
mono‑2‑ethyl 5‑carboxypentyl phthalate & MECPP & 148386 & C051450 & 1403
& DEHP \\
mono‑2‑ethyl‑5‑hydroxyhexyl phthalate & MEHHP & 170295 & C479069 & 1402
& DEHP \\
mono‑2‑ethyl‑5‑oxohexyl phthalate & MEOHP & 119096 & C080276 & 1401 &
DEHP \\
mono‑2‑ethylhexyl phthalate & MEHP & 21924291 & C016599 & Unsure &
DEHP \\
mono‑4‑methyl‑7‑hydroxyoctyl phthalate & oh-MiNP & 102401880 & NA & 1451
& NA \\
mono‑4‑methyl‑7‑oxooctyl phthalate & oxo-MiNP & 102401881 & NA & 1492 &
NA \\
mono‑iso‑butyl phthalate & MiBP & 92272 & C575690 & 1399 & DiBP \\
mono‑n‑butyl phthalate & MnBP & 8575 & C028577 & 1398 & NA \\
monoethyl phthalate & MEP & 75318 & C581825 & 1396 & DEP \\
\end{longtable}

}

\end{table}%

\subsection{Corticosteroids}\label{corticosteroids}

\begin{itemize}
\tightlist
\item
  Levels of unprocessed biomarkers (metabolites), with IDs.
\item
  Table comparing subjects with and without measurement of steroids.
\end{itemize}

\section{Main results}\label{main-results}

\begin{itemize}
\tightlist
\item
  RQ2: group chemicals by class, and for each chemical report results
  with metabolites (\texttt{avg\_comparisons} with estimate, SE,
  s-value, CI).
\item
  RQ3: report results with outcome (\texttt{avg\_comparisons} with
  estimate, SE, s-value, CI).
\end{itemize}

\section{Other analyses}\label{other-analyses}

### 2023-10-16 output/paper/sections/results.qmd
I think I fixed the cross-referencing with external files and tables at the end.

- Report number of individuals at each stage of study: numbers potentially eligible, examined for eligibility, confirmed eligible, included in the study, completing follow-up, and analysed.
- Give reasons for non-participation at each stage.
- Consider use of a flow diagram.

@@

- Give characteristics of study participants (demographic, clinical, social) and information on exposures and potential confounders.
  - Include all covariates included in primary or secondary analyses.
  - Provide detailed information about exposures' distributions: minimum and maximum, percentiles, and number of observations above/below the assay's LOD and LOQ.
- Indicate number of participants with missing data for each variable of interest.
- Cohort study: summarise follow-up time (average and total amount).

@@

- Cohort study: report numbers of outcome events or summary measures over time.
- Cross-sectional study: report numbers of outcome events or summary measures.

@@

- All results on which study conclusions or inferences are based, including null findings and results of secondary or sensitivity analyses, must be reported. Use of sub-headings that describe the nature of the results (but no declarative statements).
  - Provide a clear and concise description of all findings without extrapolating beyond the study results.
  - Do not limit results to those *statistically significant* or that support the study hypotheses. Avoid using statistical significance testing as the sole or primary criterion for interpreting the obtained results. If significance testing or *p*-values are used, report numeric *p*-values, rounded to 1-2 digits, for all results.
- Give unadjusted and confounder-adjusted estimates and their precision (e.g., $95\%$ confidence interval). Make clear which confounders were adjusted for and why they were included. Include the number of observations for each analysis after accounting for missing data. Include numeric data within figures (e.g., forest plots), or provide tables with corresponding numeric data for all figures.
- Report category boundaries when continuous variables were categorized.

>>>>

- Give reasons for non-participation at each stage.

@@

@tbl-chem-info

@@

@@

- All results on which study conclusions or inferences are based, including null findings and results of secondary or sensitivity analyses, must be reported. Use of sub-headings that describe the nature of the results (but no declarative statements).
  - Provide a clear and concise description of all findings without extrapolating beyond the study results.
  - Do not limit results to those *statistically significant* or that support the study hypotheses. Avoid using statistical significance testing as the sole or primary criterion for interpreting the obtained results. If significance testing or *p*-values are used, report numeric *p*-values, rounded to 1-2 digits, for all results.
- Give unadjusted and confounder-adjusted estimates and their precision (e.g., $95\%$ confidence interval). Make clear which confounders were adjusted for and why they were included. Include the number of observations for each analysis after accounting for missing data. Include numeric data within figures (e.g., forest plots), or provide tables with corresponding numeric data for all figures.
  - [`marginaleffects` tables](https://vincentarelbundock.github.io/marginaleffects/articles/tables.html).
- Report category boundaries when continuous variables were categorized.
